Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-06-07 paper.qmd
fixed equation prefix and citation

crossref:
  # eq-title: Equation     # (default is "")
  fig-prefix: Fig.   # (default is "Figure")
  fig-title: Fig.
  # tbl-prefix: table    # (default is "Table")
  ref-hyperlink: false # (default is true)

@@

Then @eq-impact-k becomes

@@

Of all the orbital elements, for the needs of this paper to numerically compute
the weighting function, , @fig-weighting-inclination-i, we only need
the inclination $i$. 
For debris with inclination $i$ we simulate an orbit of $N$, i.e. $10000$,
positions ($\nu$) and calculate the corresponding Cartesian positions and
the equivalent longitudes and latitudes.
The latitudes are then binned on half degree intervals to compute
$\sigma(\varphi, i)$, as per @eq-impact-probability-density.

>>>>

crossref:
  eq-prefix: ""
  fig-prefix: Fig.   # (default is "Figure")
  fig-title: Fig.
  # tbl-prefix: table    # (default is "Table")
  ref-hyperlink: false # (default is true)

@@

Then (@eq-impact-k) becomes

@@

Of all the orbital elements, for the needs of this paper to numerically compute
the weighting function, , @fig-weighting-inclination-i, we only need
the inclination $i$. 
For debris with inclination $i$ we simulate an orbit of $N$, i.e. $10000$,
positions ($\nu$) and calculate the corresponding Cartesian positions and
the equivalent longitudes and latitudes.
The latitudes are then binned on half degree intervals to compute
$\sigma(\varphi, i)$, as per (@eq-impact-probability-density).
